Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating subgenome assignments in maize

### 2017-08-11 R/SubGenome Analysis.Rmd
Minor
Back to Linux paths
Manually fixed table
Moved chr10 for both a and b into last spot in table and gave the org_chr1 column a pretty name.

```{r importSynMapData, include=FALSE}
## source("~/git/SubGenomes/R/parseSubgenomes.R")
## source("~/git/SubGenomes/R/addGOTerms.R")

source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
```

@@

# De-emphasize na's by turning them light grey
homeologs.spread.formattedTable <- homeologs.spread
homeologs.spread.formattedTable[is.na(homeologs.spread.formattedTable)] <- "<font color=\"lightgrey\">na</font>"
homeologs.spread.formattedTable %>% 
  knitr::kable(caption = "Table", 
               align = "lccccccccccr")
```

@@

>>>>

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
```

@@

# De-emphasize na's by turning them light grey
homeologs.spread.formattedTable <- data.frame(rbind(homeologs.spread[-c(2),], homeologs.spread[c(2),]))
homeologs.spread.formattedTable <- cbind(homeologs.spread.formattedTable[,-c(3, 12)], homeologs.spread.formattedTable[,c(3, 12)])
homeologs.spread.formattedTable <- rename(homeologs.spread.formattedTable, Chromosome=org_chr1)
homeologs.spread.formattedTable[is.na(homeologs.spread.formattedTable)] <- "<font color=\"lightgrey\">na</font>"
homeologs.spread.formattedTable %>% 
  knitr::kable(caption = "Table", 
               align = "lccccccccccr")
```

@@

foreach sorghum chromosome, set the largest syntenic chromosome (by gene) as sub1.  Foreach additional syntenic chromosome if doesn't overlap what is already in sub1, add it to sub1. Else, if it does not overlap anything in sub2, add to sub2.  Else toss.  After all syntenic chromosomes are process for this sorghum chromosome, count the number of genes in sub1 and sub2.  If sub2 is bigger, switch them.  *Toss out "small" syntenic chromosomes (51 genes or less?), and consider a tolerance for how much overlap must occur to consider it a true overlap.  Also consider switching to gene level overlap rather than whole-chromosome start/stop values.
